Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Extend "setting expectations"
State, that support for properties is fully functional
Wording

\noindent Or we may expect that a value satisfies some predicate.

@@

@@

@@

\noindent This can be used for any instances of Monoid.
Here is an example to apply it to a list:

>>>>

\noindent Or we may expect that a value should satisfies some
predicate.

@@

\noindent Where \verb|shouldReturn| has the following type:

@@

The implementation is fully functional, and it will be included in the
next release of Doctest.

@@

\noindent This can be used to document and automatically test
arbitrary Monoid instances.
Here is an example how to use it for lists:
